%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{4.1pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{
\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Anas Alhadi} \\ \vspace{1pt}
		\small (902)-329-9923 $|$ \label{contact_info}\href{mailto:Alhadi@dal.ca}{\underline{Alhadi@dal.ca}} $|$ 
    \href{https://linkedin.com/in/anas-alhadi}{\underline{Linkedin}}
$|$ 
    \href{https://github.com/pthread-me}{\underline{GitHub}}
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dalhousie University}{Halifax, NS}
      {Bachelor of Computer Science with Honours - GPA: 4.09/4.3}
      {Jan. 2021 -- May. 2025}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

	\resumeSubheading
      {research Assistant}{April. 2024 -- May. 2025  }
      {Dalhousie University}{Halifax, NS}
      \resumeItemListStart
        \resumeItem{Worked under Dr. Samer Lahoud, an IoT networking expert on improving\\ metadata compression in IoT packets.}
        \resumeItem{Developed the ability to efficiently grasp the contents of Documentation, RFC standards\\ and research papers.}
      \resumeItemListEnd 


    \resumeSubheading
		{Undergraduate Teaching Assistant}{Aug. 2023 -- Dec. 2024 }
      {Dalhousie University}{Halifax, NS}
      \resumeItemListStart
        \resumeItem{Managed 400+ Git repositories incorporating the use of bash scripts in the process.}
        \resumeItem{Instructed on Systems topics including  C programming, basic Computer Architecture and UNIX operations.}
        \resumeItem{Provided in-person guidance to students, ensuring clarity and comprehensiveness.}
      \resumeItemListEnd 
  \resumeSubHeadingListEnd





\section{Projects}
    \resumeSubHeadingListStart

	
	  \resumeProjectHeading
		{\textbf{KeBaB} $|$ \emph{C++}}{Aug. 2024 -- Present}
			\resumeItemListStart
			\resumeItem{\underline{Paper Title:} K-mer based breaking for finding SMEMs.
			\hfill \makebox[40pt][r]{ 
		\href{https://arxiv.org/abs/2502.20338}{\underline{Paper}}  
		 \hspace{10pt} \href{https://github.com/SuchithSridhar/Compact-DNA-Data-Structures}{\underline{Code}}
		}}
        

					\resumeItem{Collaborated with experts to implement improved algorithms used in the identification of \\ certain patterns 
						in the human genome.}
            \resumeItem{Assisted in the Testing and Debugging of a relativley large code base.}
						\resumeItem{Evaluated the performance of our implementation.}
					\resumeItemListEnd

		\resumeProjectHeading
		{\textbf{Dynamic Context Updating in SCHC} $|$ \emph{Python3}}{Jan. 2025 -- Present}
          \resumeItemListStart
					\resumeItem{\underline{Thesis Title:} Dynamic Context Updating in SCHC.
			\hfill \makebox[40pt][r]{ 
		\href{https://github.com/pthread-me/Dynamic-Context-Update-SCHC/blob/main/Thesis.pdf}{\underline{Paper}} 
			\hspace{10pt} \href{https://github.com/pthread-me/Dynamic-Context-Update-SCHC}{\underline{Code}} 
		}}
       

						\resumeItem{Completed and Defended a study on a novel, dynamic rule updating algorithm for \\an IoT based compression protocol (SCHC). }
            \resumeItem{Built a prototype of the implementation for the updating algorithm.}
            \resumeItem{Built an emulation testbed that was used to evaluate the performance of said algorithm.}
          \resumeItemListEnd


			\resumeProjectHeading
          {\textbf{Advanced Data Structures} $|$ \emph{GoLang, Python3}}{Aug. 2023 -- April. 2024}
          \resumeItemListStart
            \resumeItem{Collaborated with a classmate to implement and analyze non trivial data structures.
      	\hfill \makebox[40pt][r]{ 
			\hyperref[contact_info]{\underline{Contact}}  \hspace{10pt} \href{https://github.com/HamzaWahed/trees}{\underline{Code}}}} 
      
						\resumeItem{Implemented: Splay Trees, Van Emde Boas trees.}
            \resumeItem{Evaluated performance by stress testing the Data structures and compared results \\against the theoretical limits.}

						\resumeItemListEnd
    \resumeSubHeadingListEnd








%
%-----------PROGRAMMING SKILLS-----------

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++, Java, Python3, MySQL, GoLang, JavaScript} \\
     \textbf{Developer Tools}{: Scapy, Git, Docker, WireShark, Makefile, GDB, RiotOS } \\
     \textbf{Frameworks:}{: Flask, Espresso, JUnit, Nodejs} \\
     \textbf{Markup Languages}{: LaTeX, Markdown, HTML, CSS}
    }}
 \end{itemize}

\section{Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     
     \textbf{Sexton Scholar:}{ Awarded each semester to students with a 3.85 or higher GPA on a full course load, achieved 6 times.}
    
    \textbf{Dean's List:}{ Awarded each semester to students with a term GPA between 3.4 and 3.84 while on a full course load, achieved twice.}
    
    \textbf{Oman MoHE Scholarship:}{ Awarded to the top performing highschool students in the country, includes 4 years of paid university tuition.}
    }}
 \end{itemize}



%-------------------------------------------
\end{document}

