\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{4.1pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
			\textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{
\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}


%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Anas Alhadi} \\ \vspace{1pt}
		\vspace{5pt}
		\small (902)-329-9923 $|$ \href{mailto:anas.n.alhadi@outlook.com}{anas.n.alhadi@outlook.com} $|$ 
    \href{https://linkedin.com/in/anas-alhadi}{linkedin.com/in/anas-alhadi} $|$ 
    \href{https://github.com/pthread-me}{github.com/pthread-me}
    
\end{center}



%-----------EXPERIENCE-----------

\vspace{1pt}
\section{Experience}
	\vspace{5pt}
  \resumeSubHeadingListStart
	\resumeSubheading
      {Research Assistant}{Halifax, NS}
      {Dalhousie University}{Sep. 2024 -- May. 2025}
      \resumeItemListStart
        \resumeItem{Collaborated with colleagues and field experts in a team setting to both design and implement solutions for novel computer science problems.}
        \resumeItem{Demonstrated strong time management and organizational skills by successfully meeting multiple tight deadlines.}
				\resumeItem{Regularly explained advanced technical solutions to non-specialists in a clear and approachable manner.}
			\resumeItemListEnd 


	\vspace{15pt}
	\resumeSubheading
	{Teaching Assistant}{Halifax, NS}
      {Dalhousie University}{Aug. 2023 -- Dec. 2024}
      \resumeItemListStart
				\resumeItem{Took ownership of administrative responsibilities, in which I leveraged my technical background to automate certain tasks.}
				\resumeItem{Provided one-on-one consultations through office hours, in which I worked with students to ensure their understanding of the material and clarify any questions.}
				\resumeItem{Developed and delivered presentations on lab material, making use of slides and live demos to improve students' understanding.}
			\resumeItemListEnd 
  \resumeSubHeadingListEnd




%-----------PROGRAMMING SKILLS-----------

\vspace{5pt}
\section{Skills}
  \resumeItemListStart
		\resumeItem{\textbf{Languages:} English and Arabic, with an 11/12 score in CELPIP (Canadian English Language Proficiency).}
		\resumeItem{\textbf{Product Knowledge: }{Experience with mobile systems, cloud services, operating systems, networks, and PCs.}} \\
		\resumeItem{\textbf{Software Skills: } Experience with multiple programming languages, network protocols, and web development.}
	\resumeItemListEnd 



%-----------EDUCATION-----------
\vspace{5pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dalhousie University}{Jan. 2021 -- May. 2025}
      {Bachelor of Computer Science - First Class Honours}
      {Halifax, NS}
    
  \resumeSubHeadingListEnd


\section{Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
   
     \textbf{Dean's List:}{ Awarded each semester to students with a high GPA; achieved in ten semesters.}
    
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

