\documentclass{letter}
\usepackage{hyperref}
\signature{Anas Alhadi}
\address{1746 Henry st \\ Halifax \\ NS B3H 3K6}
\begin{document}
\longindentation=0pt


\begin{letter}{L3Harris \\ Waterdown, ON}
\opening{Dear Hiring Committee,}

Please accept my application for the embedded software developer position at the WESCAM division of your organization
(Ref\#: 23189). I am confident that my current skillset will make me a decent candidate for the position.

As part of my undergraduate honours research in which I focused on IoT based protocol compressions, I was presented with
the opertunity to work with embedded systems on the ESP32 devices in which I wrote and deployed networking level applications
using the RiotOS operating system which is a RTOS for embedded linux. Moreover, working with such systems in the context 
of networking protocols meant that I had to do a large amount of self learning by reading OS documentations, RFCs, as well as both
heavily technical and abstract research papers. 

On a more macro level, I am extremley comfortable with C and C++ with most of my programming being written in them, further I often
make use of commandline tools and premitive build systems (Makefile), thus am familiar with how these technologies work
beyond just writting the code (compliation, linking, library managemnt, etc).

With my strong work ethic, interset and knowledge in low-level programming i'm confident that the WESCAM division will make good use
of my skills and relatively quickly.

Thank you for your time and consideration. I am ethusiastic about being part of the team at L3Harris. And am looking forward to your reply.

\closing{Sincerely,}



\end{letter}
\end{document}


