\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{4.1pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
			\textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{
\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}


%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Anas Alhadi} \\ \vspace{1pt}
		\vspace{5pt}
		\small (902)-329-9923 $|$ \href{mailto:anas.n.alhadi@outlook.com}{anas.n.alhadi@outlook.com} $|$ 
    \href{https://linkedin.com/in/anas-alhadi}{linkedin.com/in/anas-alhadi} $|$ 
    \href{https://github.com/pthread-me}{github.com/pthread-me}
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dalhousie University}{Jan. 2021 -- May. 2025}
      {Bachelor of Computer Science - First Class Honours, GPA: 3.93/4}
      {Halifax, NS}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

	\resumeSubheading
      {John Hopkins University}{Sep. 2024 -- Nov. 2025}
      {Bioinformatics Research Assistant (\href{https://link.springer.com/chapter/10.1007/978-3-032-05228-5_2}{\underline{Publication}})}{Remote}
      \resumeItemListStart
        \resumeItem{Accelerated the querying operation of KeBaB, a DNA string 
          matching algorithm, from $60\mu s$ to $30\mu s$, by developing a 
          skipping optimization in the core C++ engine.
          }
        \resumeItem{Improved CPU utilization of KeBaB's preprocessing stage by $5\%$ 
          through the integration of intel's SIMD operations to the preprocessor's hashing functions.}
        \resumeItem{Automated all code validation and performance profiling, 
          significantly reducing developer workload and speeding up development 
          cycles by approximatley $20\%$,  by developing a custom Python suite that
          interfaces with the C++ code to perform unit and integration testing as well
          as benchmarking and statistical analysis.}
        \resumeItem{Delivered a complete and tested implementation of KeBaB in under 6 weeks, meeting the deadlines for the journal submission of our research paper.}
      \resumeItemListEnd 

  \resumeSubheading
		{Dalhousie University}{Apr. 2024 -- May. 2025}
      {IoT Research Assistant}{Halifax, NS}
      \resumeItemListStart
				\resumeItem{Improved compression ratios of an IoT networking protocol, SCHC, by up to 20\%, through the integration of scheduling algorithms into its rule selection scheme.}
				\resumeItem{Delivered the improved rule updating support to esp32 devices by integrating the scheduling algorithm into existing 
				implementations of SCHC in the RIOT-OS network stack.}
        \resumeItem{Automated the configuration of the IoT Lilygo devices on Linux, reducing setup times to a few seconds, 
        through the development of Bash scripts that automatically identify target devices 
        and configure their wireless modules.}
				\resumeItem{Configured a Linux-based emulation enviroment used to stress test the SCHC modifications, with 1500 different testing scenarios, ensuring a correct and robust implementation.}
			\resumeItemListEnd 


	\vspace{5pt}
	\resumeSubheading
	{Dalhousie University}{Aug. 2023 -- Dec. 2024}
      {Teaching Assistant}{Halifax, NS}
      \resumeItemListStart
				\resumeItem{Automated the setup process of weekly labs, reducing time 
          spent on creating and populating repositories from $5hrs$ to $10min$, by developing Bash scripts
          that interface with the Gitlab API to perform CRUD operations on student repositories.}
				\resumeItem{Automated the lab grading process, reducing administrative time from $2hrs$ to $30mins$, through the use of python 
        scripts to convert grades retrived of Gitlab API from JSON format to a valid CSV format.}
				\resumeItem{Led weekly classes for over $100+$ students, teaching concepts related to C programming, assembly instructions and discrete mathmatics.}
			\resumeItemListEnd 
  \resumeSubHeadingListEnd


\section{Projects}
    \resumeSubHeadingListStart
			\resumeProjectHeading
          {\textbf{Live Lyric Translation} $|$ \emph{AWS, Docker, NodeJS, Express}}{}
          \resumeItemListStart
            \resumeItem{Designed and launched a SaaS web service that provided realtime lyric translation to songs currently playing on a client's Spotify account.} 
						\resumeItem{Integrated the use of AWS Translate providing universal translation, with background
						caching of frequently accessed lyrics in S3 buckets, significantly reducing translation costs.}
          %  \resumeItem{Manually deployed all cloud resources from the provisioning of resources to the API gateway and access control configurations ensuring fine tuned control with only the minimal resource needed being used}

						\resumeItemListEnd
    \resumeSubHeadingListEnd




%-----------PROGRAMMING SKILLS-----------

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:}{ C/C++, Python, Rust, Java, JavaScript, SQL, LaTeX, HTML, CSS} \\
     \textbf{Developer Tools:}{ Git, Docker, WireShark, Makefile, AWS, GCP, GDB, Protobuf, Android Studio} \\
     \textbf{Frameworks:}{, NodeJS, Express, React, Tailwind, CTest, JUnit, PyTest} \\
    }}
 \end{itemize}

\section{Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Dean's List:}{ Awarded each semester to students with a high GPA; achieved in 10 semesters.}
    
    \textbf{Oman MoHE Scholarship:}{ 4 years of paid university tuition, awarded to the top performing high scool students.}
    }}
 \end{itemize}



%-------------------------------------------
\end{document}

